\textsc{\wobble: a data-driven method for precision radial velocities}

### 2019-01-02 paper/paper.tex
moving Rodrigo's shit
Former-commit-id: f5f09de419572b53514d6875baa2fa1007e62cae

The resulting \RV signal retrieved by \wobble is shown in Figure \ref{fig:hd189_rm}. 
We fit the signal using \starry \citep{Luger2018}, which computes analytic occultation
light curves for bodies whose surfaces can be decomposed into sums
of spherical harmonics. Since the radial component of the velocity field of a 
differentially rotating star can be expressed in terms of polynomials in 
$x = \sin\theta\cos\phi$, $y = \sin\theta\sin\phi$, and $z=\cos\theta$, where
$\theta$ is the polar angle and $\phi$ is the azimuthal angle \citep[c.f. Equation 91 in][]{Short2018},
this velocity field may be expressed exactly in terms of spherical harmonics
\citep{LugerBedell2019}.
We therefore use \starry to fit for the equatorial rotational velocity, the inclination,
the obliquity, and the shear due to differential rotation of the star, closely
following the analysis performed in \citet{Cegla2016}.
We infer a projected stellar obliquity $\lambda = -0.43 \pm 0.34^\circ$, in close agreement
with the value reported in \citet{Cegla2016}. Our inferred values for the other parameters
are broadly consistent with the results in \citet{Cegla2016}, except with significantly
higher uncertainty due to the fact that we are unable to constrain the stellar inclination
due to the $v\sin i$ degeneracy. We attribute the narrower posteriors in \citet{Cegla2016}
to a difference in the choice of prior.
\footnote{See \href{https://github.com/megbedell/wobble/tree/master/scripts/DifferentialRotationWithSphericalHarmonics.ipynb}{this interactive notebook} 
          for a derivation of the spherical harmonic decomposition of the stellar velocity field. 
          The notebook used to perform our analysis and produce Figure~\ref{fig:hd189_rm}, along with the full posterior constraints we obtain, can be found 
          \href{https://github.com/megbedell/wobble/tree/master/scripts/HD189733bWithStarry.ipynb}{here}.}

>>>>

The resulting \RV signal retrieved by \wobble is shown in Figure \ref{fig:hd189_rm}. 
We fit the signal using \starry \citep{Luger2018}, which computes analytic occultation
light curves for bodies whose surfaces can be decomposed into sums
of spherical harmonics. Since the radial component of the velocity field of a 
differentially rotating star can be expressed in terms of polynomials in 
$x = \sin\theta\cos\phi$, $y = \sin\theta\sin\phi$, and $z=\cos\theta$, where
$\theta$ is the polar angle and $\phi$ is the azimuthal angle \citep[c.f. Equation 91 in][]{Short2018},
this velocity field may be expressed exactly in terms of spherical harmonics
\citep{LugerBedell2019}.
We therefore use \starry to fit for the equatorial rotational velocity, the inclination,
the obliquity, and the shear due to differential rotation of the star, closely
following the analysis performed in \citet{Cegla2016}.
We infer a projected stellar obliquity $\lambda = -0.43 \pm 0.34^\circ$, in close agreement
with the value reported in \citet{Cegla2016}. Our inferred values for the other parameters
are broadly consistent with the results in \citet{Cegla2016}, except with significantly
higher uncertainty due to the fact that we are unable to constrain the stellar inclination
due to the $v\sin i$ degeneracy. We attribute the narrower posteriors in \citet{Cegla2016}
to a difference in the choice of prior.
\footnote{See \href{https://github.com/megbedell/wobble/tree/master/paper/figures/HD189733/DifferentialRotationWithSphericalHarmonics.ipynb}{this interactive notebook} 
          for a derivation of the spherical harmonic decomposition of the stellar velocity field. 
          The notebook used to perform our analysis and produce Figure~\ref{fig:hd189_rm}, along with the full posterior constraints we obtain, can be found 
          \href{https://github.com/megbedell/wobble/tree/master/paper/figures/HD189733/HD189733bWithStarry.ipynb}{here}.}
